% Stability-Driven Chunking for Vector Database Embeddings
% CURV Institute

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{xcolor}

% Placeholder macro for generated content
\newcommand{\placeholder}[1]{\textcolor{red}{[#1]}}

\title{Stability-Driven Chunking for Vector Database Embeddings}

\author{CURV Institute}

\date{\today}

\begin{document}

\maketitle

\begin{abstract}
\placeholder{Abstract to be generated from experimental results.}
\end{abstract}

\section{Introduction}

\placeholder{Introduction referencing PRH (arXiv:2405.07987).}

\section{Method}

\subsection{Cut-Score Formulation}

\placeholder{Cut-score algorithm description.}

\subsection{Offline Chunking}

\placeholder{Offline chunking procedure.}

\subsection{Streaming Chunking}

\placeholder{Streaming chunking procedure.}

\section{Experimental Setup}

\placeholder{Dataset, embedding model, evaluation protocol.}

\section{Results}

\subsection{Embedding Drift}

\placeholder{Drift results.}

% Include generated table
% \input{tables/drift_results.tex}

\subsection{Neighbor Churn}

\placeholder{Churn results.}

% \input{tables/churn_results.tex}

\subsection{Retrieval Stability}

\placeholder{Overlap results under reformulation.}

% \input{tables/overlap_results.tex}

\subsection{Maintenance Cost}

\placeholder{Re-embedding and rebuild metrics.}

\section{Discussion}

\placeholder{Trade-offs, limitations, relation to PRH.}

\section{Conclusion}

\placeholder{Summary consistent with measured results.}

\section*{Acknowledgments}

These diagnostics were developed as part of a broader internal CURV Institute representation-first framework; only the operational components relevant to the experiments are used here.

\bibliographystyle{plain}
\bibliography{references}

\appendix

\input{artifact_appendix}

\end{document}
